Embedded meta-learning

### 2019-04-26 writing/embedded_meta_learning.tex
Continual learning setup

%\subsection{Boolean functions}
%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs. Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input. We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs. \par   
%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
%
\subsection{Learning multivariate polynomials}
As a proof of concept, we first evaluated the system on the simple task of learning polynomials in 4 variables of degree $\leq 2$ (i.e. the task was to learn functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. \par
%% TODO: appendix
We randomly sampled the train and test polynomials as follows:
\begin{enumerate}
\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
\item Sample the subset of $k$ variables that are relevant uniformly at random.
\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random intercept drawn from $\mathcal{N}(0, 2.5)$.
\end{enumerate}
The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial. The datasets were resampled every 50 epochs of training. \par
\subsubsection{Results}

>>>>

%\subsection{Boolean functions}
%As a proof of concept, we first evaluated the system on a simple task of computing boolean functions on boolean inputs. Specifically, we can imagine mapping from binary-valued input vectors to a single binary output representing the evaluation of some logical proposition on the input. We train the system to figure out how to compute the predicate from seeing a subset of the (input, output) pairs. \par   
%We can then train the system to do various meta-mappings, for example identifying certain types of functions (like XOR) or negating predicates. \par
%
\subsection{Learning multivariate polynomials}
As a proof of concept, we first evaluated the system on the simple task of learning polynomials in 4 variables of degree $\leq 2$ (i.e. the task was to learn functions of the form $f: \mathbb{R}^4 \rightarrow \mathbb{R}$ where $f \in \mathcal{P}_2 \left(\mathbb{R}\right)$). This yields an infinite family of base-level tasks (the vector space of all such polynomials), as well as many families of meta-mappings over tasks (for example, multiplying a polynomial by a constant, squaring a polynomial, or permuting its input variables). This allows us to not only examine the ability of the system to learn to learn polynomials from data, but also to adapt its learned representations in accordance with these meta-tasks. \par
%% TODO: appendix
We randomly sampled the train and test polynomials as follows:
\begin{enumerate}
\item Sample the number of relevant variables ($k$) uniformly at random from 0 (i.e. a constant) to the total number of variables.
\item Sample the subset of $k$ variables that are relevant uniformly at random.
\item For each term combining the relevant variables (including the intercept), include the term with probability 0.5. If so give it a random intercept drawn from $\mathcal{N}(0, 2.5)$.
\end{enumerate}
The data points on which these polynomials were evaluated were sampled uniformly from $[-1, 1]$ independently for each variable, and for each polynomial. The datasets were resampled every 50 epochs of training. \par

\subsection{Continual learning}
Although the meta-learning approach is effective for rapidly adapting to a new task, it is unreasonable to think that our system must consider every example of a task it has seen at each inference step. We would like to be able to store our knowledge about the tasks in a way that allows it to be more carefully refined. Furthermore, we would like the system to be able to adapt to new tasks (that it cannot perfectly solve from examples) without catastrophically interfering with our prior knowledge \citep{McCloskey1989}. \par
A very simple solution to these problems is naturally suggested by our architecture. Specifically, task embeddings can be cached so that they don't have to be regenerated at each inference step. This also allows the potential to optimize these embeddings without altering the other parameters in the architecture, thus allowing fine-tuning on a task without seeing more examples, and without interfering with performance on any other task. That is, we can see the meta-learning step as a ``warm start'' for an optimization procedure over embeddings that are cached in memory \citep[c.f.][]{Kumaran2016}.\footnote{Note that the weights generated by the hyper network could be cached instead of the embeddings, which would be much more memory intensive but would allow even better tuning and would not require passing through the hyper network at inference time.} \par 
In this section, we demonstrate the effectiveness of this solution by training on new tasks by starting from the meta-learning network's ``guess'' at the correct task embedding, and then optimizing this embedding without altering the other parameters. We show that this yields very good results if the model has been pre-trained on a sufficient distribution of tasks. \par 
%% TODO: Baselines and the fact that something interesting is being learned
